Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-07-09 ms2.tex
cartoon figure is inserted

(Jason?)

@@

We estimate the thermal radio flux from the host star to be consistent with these observed data and by extrapolating to the lower frequency range with a simple power law:
%%%
\begin{eqnarray}
f_{\star }(\nu ) &\sim & (0.4-1.375) \times 10^{-3} ~\mbox{Jy} \\
&& \times \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
\end{eqnarray}
%%%
If we assume $\alpha = 0.6$ based on constant property wind model \citep{wright1975,panagia1975,olnon1975}, radio flux at 10~pc from 10~MHz to 1~GHz is $\sim$ 25 $\mu$Jy-1 mJy, which is below the estimated radio flux of RGHJs. 
Note that it has also been suggested that the power index $\alpha $ is steeper than 0.6 \citep{gorman2013}, in which case the radio flux from the host star would be even lower.

>>>>

@@

We estimate the thermal radio flux from the host star to be consistent with these observed data and by extrapolating to the lower frequency range with a simple power law:
%%%
\begin{eqnarray}
f_{\star }(\nu ) &\sim & (0.4-1.375) \times 10^{-3} ~\mbox{Jy} \\
&& \times \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
\end{eqnarray}
%%%
Constant property wind model \citep{wright1975,panagia1975,olnon1975} predicts $\alpha = 0.6$, while observations suggested that the power index $\alpha $ is steeper than 0.6 \citep{gorman2013}. 
Figure \ref{fig:cartoon} show a cartoon for a radio spectrum of a Jovian-mass RGHJs and that of the host red giant stars with 100 $R_{\odot }$, both of which is placed at 10 pc away.  
As this figure indicates, the radio emission from RGHJs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{cartoon.pdf}
   \caption{A cartoon of radio emission spectra of a Jovian-mass RGHJ and the host red giants with 100 $R_{\odot }$. The spectrum of RGHJ is modeled after Jovian radio spectra \citep[][e.g.]{zarka2004}, while that of the host red giant is obtained simply by extrapolating observed radio spectra above 1~GHz with power law. }
  \label{fig:cartoon}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
